
\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Jordan J. Stadler}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{Jordan J. Stadler}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  MSc Candidate (Computer Science) \\
  Faculty of Science \\
 \href{http://www.uoit.ca/}{University of Ontario Institute of Technology} \\
  Oshawa, ON, Canada
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (905) 721-8668 x 2387\\
    Fax: &  (905) 721-3304 \\
    Email: & \href{mailto:jordan.stadler@uoit.ca}{\tt jordan.stadler@uoit.ca} \\
    Homepage: & \href{http://jordanstadler.com/}{\tt http://jordanstadler.com/} \\
  \end{tabular}
\end{minipage}


\section*{Education}

\begin{itemize}
  \item \textbf{M.Sc.}, Computer Science, Expected Graduation Fall 2014,\\*
    University of Ontario Institute of Technology, Oshawa, Ontario, Canada.
  \item\textbf{B.Sc.}, Computing Science (Honors), Graduated Spring 2012,\\*
    University of Ontario Institute of Technology, Oshawa, Ontario, Canada.
\end{itemize}

\section*{Research Interests}
\begin{itemize}
\item Computer vision, computer graphics, activity recognition, crowd simulation, 
crowd behavior, artificial intelligence, path finding and autonomous agent 
navigation, smart cameras, embedded vision, RGB-D, motion analysis.
\end{itemize}

\section*{Research Experience}
\begin{itemize}
\item \textbf{Graduate Research}, University of Ontario Institute of Technology, 2012-Present.
  \begin{itemize}
	  \item Graduate research completed with a focus in computer vision and computer graphics.  Graduate thesis work in the application of
      optical flow based crowd analysis for data-driven virtual crowd synthesis and computer vision based crowd comparison.
    \item Tools: C++, Python, MATLAB, OpenCV, RVO2, Unity 3D
  \end{itemize}
\item \textbf{Undergraduate Summer Research}, University of Ontario Institute of Technology,  Summer 2012.
  \begin{itemize}
	\item Undergraduate summer research involved activity recognition and analysis using Microsoft Kinect.  Common cause of retirement for Fire Fighters in lower back injuries.  Incorrect lifting encourages these types of injuries.  Using RGB-D streams provided by Kinect we
  analyze users performing various lifts and provide feedback based on users actions.  The goal was to provide the back end for a serious game.  Joint project with Game Development in the Faculty of Business and IT. Funded by the Canadian Memorial Chiropractic College, Ontario Workplace and Insurance Board, and Toronto Fire Services.
  \item Tools: C++, OpenNI, OpenCV, libSVM, Weka, PCL
  \end{itemize}
\item \textbf{Undergraduate Thesis}, University of Ontario Institute of Technology, 2011-2012.
  \begin{itemize}
	  \item Undergraduate thesis project with a focus in computer vision.  Created an interactive panoramic image stitching application for use with webcams. Users are able to use a variety of modes to accomplish a panoramic image stitch which is created live.
    \item Tools: C++, OpenCV, Boost
  \end{itemize}
\end{itemize}


\section*{Teaching Experience}
\begin{itemize}
\item\textbf{University of Ontario Institute of Technology}
\item\textit{Guest Lecturer}
	\begin{itemize}
	\item Simulation and Modeling, CSCI 3010U, Winter 2014
 	\item Computer Architecture I, CSCI 2050U, Winter 2013
	\end{itemize}
\item\textit{Teaching Assistant}
	\begin{itemize}
	\item Simulation and Modeling, CSCI 3010U, Winter 2014
	\item Programming Workshop, CSCI 1060U, Winter 2014
	\item Advanced Computer Graphics, CSCI 4110U, Fall 2013
	\item Introduction to Computer Science with Python, CSCI 1040U, Fall 2013
	\item Digital Media Production, CSCI 3220U, Winter 2013
	\item Introduction to Computer Science with Python, CSCI 1040U, Winter 2013
	\item Introduction to Computer Science with Python (2 sections), CSCI 1040U, Fall 2012
	\end{itemize}
\end{itemize}


\section*{Graduate Courses}
\begin{itemize}
\item\textbf{Computer Communication Networks}, CSCI 5300G, Winter 2014
\item\textbf{Advanced Topics in Digital Media}, CSCI 6520G, Winter 2013
\item\textbf{Collaborative Design and Research}, CSCI 5020G, Winter 2013
\item\textbf{Computer Graphics}, CSCI 5510G, Fall 2012
\item\textbf{Survey of Computer Science}, CSCI 5010G, Fall 2012
\end{itemize}


\section*{Extracurricular and Volunteer Experience}
\begin{itemize}
\item Science Rendezvous at UOIT Volunteer, Computer Science, May 2014
\item UOIT Open House Volunteer, Faculty of Science, Winter 2014
\item UOIT Open House Volunteer, Faculty of Science, Fall 2013
\item Science Rendezvous at UOIT Volunteer, Computer Science, May 2013
\item UOIT Open House Volunteer, Faculty of Science, Winter 2013
\item UOIT Open House Volunteer, Faculty of Science, Fall 2012
\item Presented to the Board of Governors, Presented research to UOIT board of governors, 2012.
\end{itemize}


\section*{Honors and Awards}
\begin{itemize}
\item Dean's List, 2009.
\end{itemize}

\section*{Skills}
  \begin{itemize}
    \item \textbf{Languages:} C/C++ (7 years), GLSL(3 years), Python(5 years), 
    Java (9 years), BASH (5 years),  Javascript (2 years), HTML/CSS (10 years), 
    LaTeX (5 years), MATLAB (3 years)
    \item \textbf{Libraries:} OpenGL, RVO2, OpenCV, OpenNI, libSVM, PCL
    \item \textbf{IDEs:}  Visual Studio, Eclipse, Unity
    \item \textbf{Tools:}  Weka, Unix utilities
  \end{itemize}

\section*{Interests and Hobbies}
\begin{itemize}
\item Running and obstacle based courses, reading, fishing, photography, Linux, tinkering.
\item 
\end{itemize}


\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
